Supplementary Information

### 2021-02-08 doc/manuscript/MEE_manuscript.Rmd
update schematic

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer L. Baltzer^wl^,
Patrick J. Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart J. Davies^2^,
Cameron Dow^1^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Camille Piponiot^1,2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

@@

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; Front Royal, VA 22630, USA

@@

3. The Morton Arboretum, Lisle, Illinois, USA

4. Harvard Forest, Petersham, MA 01366, USA

@@

![**Figure 1 | Schematic illustrating our analysis process.** In step 1,the R package *climwin* [@van_de_pol_identifying_2016] is used to identify the most important climate drivers in water and temperature variable groups for each site. In step 2, a GLS model is used to produce a combined model with drivers, reconstructed DBH, and year.  (STILL NEED TO FIX THE PLOTS ON THIS.)](tables_figures/schematic_figure.png)

>>>>

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer L. Baltzer^wl^,
Patrick J. Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart J. Davies^2^,
Cameron Dow^1^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Camille Piponiot^1,2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

@@

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; Front Royal, Virginia 22630, USA

@@

3. The Morton Arboretum, Center for Tree Science, Lisle, Illinois 60532 USA

4. Harvard University, Petersham, Massachusetts 01366 USA

5. Midwest Dendro LLC, Naperville, Illinois 60565 USA

@@

![**Figure 1 | Schematic illustrating our analysis process.** In step 1, the R package *climwin* [@van_de_pol_identifying_2016] is used to identify the most important climate drivers in water and temperature variable groups for each site, defined as the variable-time window combination that are most strongly correlated to the residual variation around splines fit to trends in growth (here, ring width, $RW$) for all cores sampled at the site. In step 2, a GLS model is used to produce a combined model with the previously identified drivers, reconstructed DBH, and year.](tables_figures/schematic_figure.png)
